Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-25 paper.qmd
Updated Figure 13 NLDR layouts

trimesh_removed_gau_tsne <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = tsne_gau_scaled,
    aes(
      x = tSNE1,
      y = tSNE2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  coord_fixed() +
  interior_annotation("a1", 
                      position = c(0.08, 0.95),
                      cex = 2)

@@

trimesh_removed_gau_umap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = umap_gau_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  coord_fixed() +
  interior_annotation("b1", 
                      position = c(0.06, 0.95),
                      cex = 2)

@@

trimesh_removed_gau_pacmap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = pacmap_gau_scaled,
    aes(
      x = PaCMAP1,
      y = PaCMAP2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  coord_fixed() +
  interior_annotation("c1", 
                      position = c(0.08, 0.95),
                      cex = 2)

>>>>

trimesh_removed_gau_tsne <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = tsne_gau_scaled,
    aes(
      x = tSNE1,
      y = tSNE2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  interior_annotation("a1", 
                      position = c(0.08, 0.95),
                      cex = 2) +
  theme(
    aspect.ratio = 1
  )

@@

trimesh_removed_gau_umap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = umap_gau_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  interior_annotation("b1", 
                      position = c(0.06, 0.95),
                      cex = 2) +
  theme(
    aspect.ratio = 1
  )

@@

trimesh_removed_gau_pacmap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = pacmap_gau_scaled,
    aes(
      x = PaCMAP1,
      y = PaCMAP2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  interior_annotation("c1", 
                      position = c(0.08, 0.95),
                      cex = 2) +
  theme(
    aspect.ratio = 1
  )
